---
title: "TEMPLATE TITLE REPORT"
author: "Jonathan Chan"
date: "2026-01-07"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{css theme-override, echo = FALSE}
.page-header {
    background-image: linear-gradient(120deg, 
#6bbc42, #42742a);
}
.main-content h1,
.main-content h2,
.main-content h3,
.main-content h4,
.main-content h5,
.main-content h6 {
    color: #42742a
}

```

```{r setup, include=FALSE}
# install.packages("devtools")
# require(devtools)
# install_github("lchiffon/wordcloud2")
# Install.packages("tm")

library(ggplot2)
library(readxl)
library(tidyverse)
library(scales) # for percentage 
# library(wordcloud2) # for wordcloud
library(RColorBrewer) #for color schemes
library(tm)


#GLOBAL OPTIONS: don't show code, results,  and warnings 
### DEBUG MOD: 
# knitr::opts_chunk$set(echo = FALSE,
#                       results=TRUE,
#                       warning=TRUE)
### USE BELOW WHEN CREATING FINAL CHART: don't show code, results,  and warnings 
knitr::opts_chunk$set(echo = FALSE,
                      results=FALSE,
                      warning=FALSE)

#remove scientific notation
options(scipen=999)
```


```{r import survey, echo=FALSE,results='hide',message=FALSE}

# file_path <- "data/EXCEL_FILENAME_HERE.xlsx"
# sheet_names <- excel_sheets(path = file_path)

### If multiple sheets, use this fn to get 
# raw_dfs <- lapply(sheet_names, function(sheet_name) {
#   read_excel(file_path, sheet = sheet_name)
# })

```

### Insert 

```{r final_vars}
### Set p1, p2, p3 to the ggplot variables

kpi1 <- "100"
kpi2 <- "200"
kpi3 <- "300"

kpi1 <- as.character(kpi1)
kpi2 <- as.character(kpi2)
kpi3 <- as.character(kpi3)

```

# TEST TITLE

Goal: Show the key research question.

Steps:


1. data wrangle using cells above header title
2. Put display plot variables - p1, p2, p3 - to show graphs
3. show tables using knitr::kable() to show agg tables (use head or wrangle to be less than a few cols)
4. 3 key findings using Sub header and `r as.character("variable")` to show variables in R markdown report


### Key finding 1:  The program supported a total of **`r kpi1`** seniors in aging at home, **`r kpi2`** of which were new seniors to the program.

```{r fig.show="hold", results=TRUE}
#p1
# knitr::kable(kpi_totals)
```

###### INSERT FOOTNOTE HERE
###### INSERT DATE LAST UPDATED